---
title: "HELMi metaData distribution"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r, warning=FALSE, echo=FALSE, message=FALSE}
# libraries
library("readxl")
library("tidyverse")
library("ggridges")

# Load the spreadsheets
Voc <- read_excel("../questionnaire_vocabulary.xlsx")

Q1_max<-1055
Q1 <- read_csv("../normalized_versions/corrected_translated/Q1_norm_background_04.10.18.csv", guess_max=Q1_max) %>% 
  add_column(questionnaire="A_background")

Q2_max<-7242
Q2 <- read_csv("../normalized_versions/corrected_translated/Q2_norm_Previous3months_15.08.20.csv", guess_max=Q2_max) %>% 
  add_column(questionnaire="E_Previous3Months")

Q3_max<-6653
Q3 <- read_csv("../normalized_versions/corrected_translated/Q3_norm_4to6months_26.01.20.csv", guess_max=Q3_max) %>% 
  add_column(questionnaire="C_4to6months")

Q4_max<-5600
Q4 <- read_csv("../normalized_versions/corrected_translated/Q4_norm_7to12months_27.01.21.csv", guess_max=Q4_max) %>% 
  add_column(questionnaire="D_7to12months")

Q5y1_max<-431
Q5y2_max<-901
Q5y1B_max<-532
Q5y2B_max<-6
Q5y1 <- read_csv("../normalized_versions/corrected_translated/Q5_norm_NutritionMotorDev_v2_yearI_28.01.21.csv", guess_max=Q5y1_max) %>% 
  add_column(questionnaire="F1_NutritionMotorDev_year1_Version2")
Q5y2 <- read_csv("../normalized_versions/corrected_translated/Q5_norm_NutritionMotorDev_v2_yearII_28.01.21.csv", guess_max=Q5y2_max) %>% 
  add_column(questionnaire="F2_NutritionMotorDev_year2_Version2")
Q5y1B <- read_csv("../normalized_versions/corrected_translated/Q5_norm_NutritionMotorDev_yearI_27.01.21.csv", guess_max=Q5y1B_max) %>%
  add_column(questionnaire="F1_NutritionMotorDev_year1_Version1")
Q5y2B <- read_csv("../normalized_versions/corrected_translated/Q5_norm_NutritionMotorDev_yearII_28.01.21.csv", guess_max=Q5y2B_max) %>% 
  add_column(questionnaire="F2_NutritionMotorDev_year2_Version1")

Q6F_max<-1018
Q6M_max<-1357
Q6F <- read_csv("../normalized_versions/corrected_translated/Q6_norm_ParentsF_FoodFrequency_28.01.21.csv", guess_max=Q6F_max) %>% 
  add_column(questionnaire="G_ParentF_FoodFrequency")
Q6M <- read_csv("../normalized_versions/corrected_translated/Q6_norm_ParentsM_FoodFrequency_28.01.21.csv", guess_max=Q6M_max) %>% 
  add_column(questionnaire="G_ParentM_FoodFrequency")

Q7_max<-683
Q7 <- read_csv("../normalized_versions/corrected_translated/Q7_norm_depression_unkown.csv", guess_max=Q7_max) %>% 
  add_column(questionnaire="G_MotherDepression")

Q8_max<-268
Q8 <- read_csv("../normalized_versions/corrected_translated/Q8_norm_HouseDustCollection_28.01.21.csv", guess_max=Q8_max) %>% 
  add_column(questionnaire="H_HouseCollection")

Q9_max<-16953
Q9 <- read_csv("../normalized_versions/corrected_translated/Q9_norm_0to3 months_02.02.2020.csv", guess_max=Q9_max) %>% 
  add_column(questionnaire="B_0to3months")

Q10y0_max<-1076
Q10y2_max<-689
Q10y0 <- read_csv("../normalized_versions/corrected_translated/Q10_norm_MotherStress_Year0_02.09.21.csv", guess_max=Q10y0_max) %>% 
  add_column(questionnaire="G0_MotherStress")
Q10y2 <- read_csv("../normalized_versions/corrected_translated/Q10_norm_MotherStress_Year2_02.09.21.csv", guess_max=Q10y2_max) %>% 
  add_column(questionnaire="G2_MotherStress")

```

# Goals and objectives: 
This documents aims to provide an overview on the HELMi contextual dataset extracted from the families questionnaires.

The following aspects are considered: 

- Distributions and outliers 

# Dataset description:

**infants questionnaires:**

- A_background
 
- F1_NutritionMotorDev_year1_version1 or F1_NutritionMotorDev_year1_version2
 
- F2_NutritionMotorDev_year2_version1 or F2_NutritionMotorDev_year2_version2

**infants frequency questionnaires:**

- E_Previous3Months
 
- C_4to6months
 
- D_7to12months
 
- B_0to3months

**parents questionnaires:**

- G_ParentF_FoodFrequency
 
- G_ParentM_FoodFrequency
 
- G_MotherDepression
 
- G0_MotherStress and G2_MotherStress

**Other questionnaires:**

- H_HouseCollection

\pagebreak 

# G_ParentF_FoodFrequency 

## Boolean fields

No boolean fields

## Categorical fields

```{r,  echo=FALSE}
curr_Voc <- Voc %>% filter(Questionnaire=="G_ParentsF_FoodFrequency")

# Looking at boolean fields
cat_fields <- curr_Voc %>% filter(data_type=="categorical") %>%
  pull(variable_short_name)
curr_cat <- Q6F %>% select(familly_ID, all_of(cat_fields)) %>% mutate_all(as.character)
curr_cat_long <- curr_cat %>% pivot_longer(!familly_ID, names_to="question", values_to="answers") 
curr_cat_counts <- curr_cat_long %>% group_by(question, answers) %>% tally() 


# categories from 1 to 10
plotcat <- curr_cat_counts %>% ggplot(aes(x=question, y=n, fill=answers)) +
  geom_bar(stat="identity")+
  coord_flip() +
  theme(legend.position="bottom",
        text = element_text(size=10))

plotcat


```
## Numerical fields

```{r,  warning=FALSE, echo=FALSE, message=FALSE, fig.height=20}
curr_Voc <- Voc %>% filter(Questionnaire=="G_ParentsF_FoodFrequency")

# Looking at int fields
int_fields <- curr_Voc %>% filter(data_type=="int") %>% 
  filter(variable_short_name != "inf_Age") %>%
  filter(variable_short_name != "inf_AgeDays") %>%
  filter(variable_short_name != "inf_AgeWeeks") %>%
  filter(usability!="EMPTY") %>%
  
  
  pull(variable_short_name)

curr_int <- Q6F %>% select(all_of(int_fields)) %>% 
  mutate_if(is.character,as.numeric)


ggplot(gather(curr_int), aes(value)) + 
    geom_histogram() + 
    facet_wrap(~key, scales = 'free', ncol = 6)

# checking type of data
type_check <-  curr_int %>% 
    dplyr::summarise_all(class) %>% 
    tidyr::gather(variable, class)


```

# G_ParentM_FoodFrequency 

## Boolean fields

No boolean fields

## Categorical fields

```{r,  echo=FALSE}
curr_Voc <- Voc %>% filter(Questionnaire=="G_ParentsM_FoodFrequency")

# Looking at boolean fields
cat_fields <- curr_Voc %>% filter(data_type=="categorical") %>%
  pull(variable_short_name)
curr_cat <- Q6M %>% select(familly_ID, all_of(cat_fields)) %>% mutate_all(as.character)
curr_cat_long <- curr_cat %>% pivot_longer(!familly_ID, names_to="question", values_to="answers") 
curr_cat_counts <- curr_cat_long %>% group_by(question, answers) %>% tally() 


# categories from 1 to 10
plotcat <- curr_cat_counts %>% ggplot(aes(x=question, y=n, fill=answers)) +
  geom_bar(stat="identity")+
  coord_flip() +
  theme(legend.position="bottom",
        text = element_text(size=10))

plotcat


```
## Numerical fields

```{r,  warning=FALSE, echo=FALSE, message=FALSE, fig.height=20}
curr_Voc <- Voc %>% filter(Questionnaire=="G_ParentsM_FoodFrequency")

# Looking at int fields
int_fields <- curr_Voc %>% filter(data_type=="int") %>% 
  filter(variable_short_name != "inf_Age") %>%
  filter(variable_short_name != "inf_AgeDays") %>%
  filter(variable_short_name != "inf_AgeWeeks") %>%
  filter(usability!="EMPTY") %>%
  
  
  pull(variable_short_name)

curr_int <- Q6M %>% select(all_of(int_fields)) %>% 
  mutate_if(is.character,as.numeric)


ggplot(gather(curr_int), aes(value)) + 
    geom_histogram() + 
    facet_wrap(~key, scales = 'free', ncol = 6)

# checking type of data
type_check <-  curr_int %>% 
    dplyr::summarise_all(class) %>% 
    tidyr::gather(variable, class)


```

# G_MotherDepression

## Boolean fields

No boolean fields

## Categorical fields

```{r,  echo=FALSE}
curr_Voc <- Voc %>% filter(Questionnaire=="G_MotherDepression")

# Looking at boolean fields
cat_fields <- curr_Voc %>% filter(data_type=="categorical") %>%
  pull(variable_short_name)
curr_cat <- Q7 %>% select(familly_ID, all_of(cat_fields)) %>% mutate_all(as.character)
curr_cat_long <- curr_cat %>% pivot_longer(!familly_ID, names_to="question", values_to="answers") 
curr_cat_counts <- curr_cat_long %>% group_by(question, answers) %>% tally() 


# categories from 1 to 10
plotcat <- curr_cat_counts %>% ggplot(aes(x=question, y=n, fill=answers)) +
  geom_bar(stat="identity")+
  coord_flip() +
  theme(legend.position="bottom",
        text = element_text(size=10))

plotcat


```
## Numerical fields

```{r,  warning=FALSE, echo=FALSE, message=FALSE, fig.height=5}
curr_Voc <- Voc %>% filter(Questionnaire=="G_MotherDepression")

# Looking at int fields
int_fields <- curr_Voc %>% filter(data_type=="int") %>% 
  filter(variable_short_name != "inf_Age") %>%
  filter(variable_short_name != "inf_AgeDays") %>%
  filter(variable_short_name != "inf_AgeWeeks") %>%
  filter(usability!="EMPTY") %>%
  
  
  pull(variable_short_name)

curr_int <- Q7 %>% select(all_of(int_fields)) %>% 
  mutate_if(is.character,as.numeric)


ggplot(gather(curr_int), aes(value)) + 
    geom_histogram() + 
    facet_wrap(~key, scales = 'free', ncol = 6)

# checking type of data
type_check <-  curr_int %>% 
    dplyr::summarise_all(class) %>% 
    tidyr::gather(variable, class)


```

# G0_MotherStress

## Boolean fields

No boolean fields

## Categorical fields

No categorical fields

## Numerical fields

```{r,  warning=FALSE, echo=FALSE, message=FALSE, fig.height=2}
curr_Voc <- Voc %>% filter(Questionnaire=="G0_MotherStress")

# Looking at int fields
int_fields <- curr_Voc %>% filter(data_type=="int") %>% 
  filter(variable_short_name != "inf_Age") %>%
  filter(variable_short_name != "inf_AgeDays") %>%
  filter(variable_short_name != "inf_AgeWeeks") %>%
  filter(usability!="EMPTY") %>%
  
  
  pull(variable_short_name)

curr_int <- Q10y0 %>% select(all_of(int_fields)) %>% 
  mutate_if(is.character,as.numeric)


ggplot(gather(curr_int), aes(value)) + 
    geom_histogram() + 
    facet_wrap(~key, scales = 'free', ncol = 6)

# checking type of data
type_check <-  curr_int %>% 
    dplyr::summarise_all(class) %>% 
    tidyr::gather(variable, class)


```

# G2_MotherStress

## Boolean fields

No boolean fields

## Categorical fields

No categorical fields

## Numerical fields

```{r,  warning=FALSE, echo=FALSE, message=FALSE, fig.height=2}
curr_Voc <- Voc %>% filter(Questionnaire=="G2_MotherStress")

# Looking at int fields
int_fields <- curr_Voc %>% filter(data_type=="int") %>% 
  filter(variable_short_name != "inf_Age") %>%
  filter(variable_short_name != "inf_AgeDays") %>%
  filter(variable_short_name != "inf_AgeWeeks") %>%
  filter(usability!="EMPTY") %>%
  
  
  pull(variable_short_name)

curr_int <- Q10y2 %>% select(all_of(int_fields)) %>% 
  mutate_if(is.character,as.numeric)


ggplot(gather(curr_int), aes(value)) + 
    geom_histogram() + 
    facet_wrap(~key, scales = 'free', ncol = 6)

# checking type of data
type_check <-  curr_int %>% 
    dplyr::summarise_all(class) %>% 
    tidyr::gather(variable, class)


```

# H_HouseCollection

## Boolean fields

```{r, echo=FALSE}
curr_Voc <- Voc %>% filter(Questionnaire=="H_HouseDust")

# Looking at boolean fields
bool_fields <- curr_Voc %>% filter(data_type=="bool") %>% pull(variable_short_name)
curr_bool <- Q8 %>% select(familly_ID, all_of(bool_fields))
curr_bool_long <- curr_bool %>% pivot_longer(!familly_ID, names_to="question", values_to="answers")
curr_bool_counts <- curr_bool_long %>% group_by(question, answers) %>% tally()

plotbools <- curr_bool_counts %>% ggplot(aes(x=question, y=n, fill=answers)) +
  geom_bar(stat="identity")+
  coord_flip() +
  theme(legend.position="bottom",
        text = element_text(size=10))

plotbools

```

## Categorical fields


```{r,  echo=FALSE}
curr_Voc <- Voc %>% filter(Questionnaire=="H_HouseDust")

# Looking at categorical fields
cat_fields <- curr_Voc %>% filter(data_type=="categorical") %>%
  pull(variable_short_name)
curr_cat <- Q8 %>% select(familly_ID, all_of(cat_fields)) %>% mutate_all(as.character)
curr_cat_long <- curr_cat %>% pivot_longer(!familly_ID, names_to="question", values_to="answers") 
curr_cat_counts <- curr_cat_long %>% group_by(question, answers) %>% tally() 


# categories from 1 to 10
plotcat <- curr_cat_counts %>% ggplot(aes(x=question, y=n, fill=answers)) +
  geom_bar(stat="identity")+
  coord_flip() +
  theme(legend.position="bottom",
        text = element_text(size=10))

plotcat


```
## Numerical fields

```{r,  warning=FALSE, echo=FALSE, message=FALSE, fig.height=2}
curr_Voc <- Voc %>% filter(Questionnaire=="H_HouseDust")

# Looking at int fields
int_fields <- curr_Voc %>% filter(data_type=="int") %>% 
  filter(variable_short_name != "inf_Age") %>%
  filter(variable_short_name != "inf_AgeDays") %>%
  filter(variable_short_name != "inf_AgeWeeks") %>%
  filter(usability!="EMPTY") %>%
  
  
  pull(variable_short_name)

curr_int <- Q8 %>% select(all_of(int_fields)) %>% 
  mutate_if(is.character,as.numeric)


ggplot(gather(curr_int), aes(value)) + 
    geom_histogram() + 
    facet_wrap(~key, scales = 'free', ncol = 3)

# checking type of data
type_check <-  curr_int %>% 
    dplyr::summarise_all(class) %>% 
    tidyr::gather(variable, class)


```

